A Few Easy Pieces: \\ How to enhance your relationship with your future self.

### 2011-03-14 workflow.Rnw
moving Type Don't Click up
Order is now type, comment, sweave, data, rest.

good.df<-na.omit(dem.nations.df[,c("Gini2004","protac2000","Nation","meanpr")])
@.

@@

A given analysis of a given collection is a long series of
decisions. You need to be able to justify them. Often you justify them
in the paper you are writing (in the text surrounding the R code
chunks in your Sweave document). Some decisions will be too small and
technical for inclusion in the paper itself. These need to be
documented in the code itself.

Using R within Sweave, for example, the comment is marked using the
pound sign. Notice that I've left in a regression not run for the
paper directly, but run as a part of the due diligence process of
writing the paper.

@@

\section{Type, don't click.}

Now, in the future if I wonder how ``that plot on page 10'' was
created, if I suitably commented my manuscript or inserted text into
my MANIFEST.txt file I will know (1) ``that plot'' is from a file
called ``fig1.pdf'' and (2) fig1.pdf was created in
\Verb+figs1and2.R+. In the future, if I wanted to quickly change
fig1.pdf, I could edit the commands quickly and easily to do
so. Another good practice is to name the files descriptively, so that
we don't in fact have ``fig1.pdf'' but ``political participation by
education in the south.pdf'' although such a name may prove burdensome
to operating systems which do not care for spaces in file names or to
folks who are used to typing full filenames rather than using command
line completion facilities in modern shells.

An even nicer way to ensure that figures and tables are reproducible
or easily modifiable by your older and wiser but more harried self is
to use literate programming. For example, to produce the
Figure~\ref{fig:giniprot}, I insert the following chunk of code into
the LaTeX document, and then I asked R to process the document, and
then produce a pdf file in which the code has disappeared to be
replaced with an actual figure.\footnote{One can insert the same code
  chunk in an OpenOffice document and use the odfWeave package to
  produce OpenOffice documents in which figures and tables replace
  code. One may also use the LyX interface to LaTeX to write LaTeX
  documents within a WYSIWYG environment.}

>>>>

good.df<-na.omit(dem.nations.df[,c("Gini2004","protac2000","Nation","meanpr")])
@.
\section{Type, don't click.}

Now, in the future if I wonder how ``that plot on page 10'' was
created, if I suitably commented my manuscript or inserted text into
my MANIFEST.txt file I will know (1) ``that plot'' is from a file
called ``fig1.pdf'' and (2) fig1.pdf was created in
\Verb+figs1and2.R+. In the future, if I wanted to quickly change
fig1.pdf, I could edit the commands quickly and easily to do
so. Another good practice is to name the files descriptively, so that
we don't in fact have ``fig1.pdf'' but
``political-participation-by-education-in-the-south.pdf''. Now, if Figure is
moved to an appendix, the file name is still meaningful.

% An even nicer way to ensure that figures and tables are reproducible
% or easily modifiable by your older and wiser but more harried self is
% to use literate programming. For example, to produce the
% Figure~\ref{fig:giniprot}, I insert the following chunk of code into
% the LaTeX document, and then I asked R to process the document, and
% then produce a pdf file in which the code has disappeared to be
% replaced with an actual figure.\footnote{One can insert the same code
%   chunk in an OpenOffice document and use the odfWeave package to
%   produce OpenOffice documents in which figures and tables replace
%   code. One may also use the LyX interface to LaTeX to write LaTeX
%   documents within a WYSIWYG environment.}

@@

A given analysis of a given collection is a long series of
decisions. You need to be able to justify them. Often you justify them
in the body of the paper you are writing. Some decisions will be too small and
technical for inclusion in the paper itself. These need to be
documented in the code itself.

Using R, for example, the comment is marked using the
pound sign. Notice that I've left in a regression not run for the
paper directly, but run as a part of the due diligence process of
writing the paper.

@@
